sensi_an_rotations201911. To analyse rotation runs for paper

### 2019-11-11 inst/documents/sensi_an_rotations201911.Rmd
plotting 16 expts

@@

    print( ggplot(df_res_all, aes(x=rot_minus_seq)) +

             geom_histogram(binwidth=10) +
             xlab('rot_minus_seq : rotation generations minus sequence') +
             ylab('count (sqrt scale to show low values)') +
             scale_y_sqrt(breaks=c(0,10,20,50,200,500,2000,5000)) + #can't use log scale because anchored at 0
             theme_minimal() +
             theme(panel.grid.minor.y=element_blank()))

>>>>

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}

# sam is running all 16 scenarios with a single outfile
# but in the meantime can I read the rda's in individually ?
# e.g. need to be able to find files named like this
# 2019-11-05-10-42-df_res_all_rotA210000.rda
# how to get all combinations of A-D and 1-4
id_columns <- expand.grid(c("A","B","C","D"),c(1:4))
expt_ids <- paste0(id_columns[,1], id_columns[,2])
#i think that if I add the 10000 in I can find the unique files
expt_ids <- paste0(expt_ids,10000)

#list all files
#list.files(infolder)

#list files matching a pattern, now get just on matching each
#list.files(infolder,"A110000")

df_res_16 <- data.frame(stringsAsFactors=FALSE)

# read in all 16 files, rbind and add ID columns
for(i in 1:length(expt_ids))
{

  # gets loaded as df_res_all because that is what it was saved as
  load(paste0(infolder, list.files(infolder, expt_ids[i])))
  # add experiment ids, first as separate columns to make facetting easier maybe
  df_res_all$idAD <- substr(expt_ids[i],1,1)
  df_res_all$id14 <- substr(expt_ids[i],2,2)

  df_res_16 <- rbind(df_res_16, df_res_all)

save(df_res_16, file=paste0(infolder,'df_res_16.rda'))

@@

    # print( ggplot(df_res_all, aes(x=rot_minus_seq)) + 
    #          
    #          geom_histogram(binwidth=10) +
    #          xlab('rot_minus_seq : rotation generations minus sequence') +
    #          ylab('count (sqrt scale to show low values)') +
    #          scale_y_sqrt(breaks=c(0,10,20,50,200,500,2000,5000)) + #can't use log scale because anchored at 0
    #          theme_minimal() +
    #          theme(panel.grid.minor.y=element_blank()))

# no colour ??
# ggplot(df_res_all, aes(x=rot_minus_seq, colour=rot_minus_seq)) + 
#      geom_histogram(binwidth=10) + 
#      scale_color_brewer(palette="Dark2")

#GOOD setting colours so can see easier when rot or seq better

widthbin <- 10 #either 10 or 20 looks fairly similar

# df_res_all$best_strategy <- ifelse(df_res_all$rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_all$rot_minus_seq > (widthbin/2), "rotation", "no_difference"))
# 
# ggplot(df_res_all, aes(x=rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=widthbin, colour='white') + 
#      theme_minimal() +
#      theme(panel.grid.minor.y=element_blank())

df_res_16$best_strategy <- ifelse(df_res_16$rot_minus_seq <= -(widthbin/2),"sequence", ifelse(df_res_16$rot_minus_seq > (widthbin/2), "rotation", "no_difference"))

# plot all 160k runs together
# ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=widthbin, colour='white') + 
#      theme_minimal() +
#      theme(panel.grid.minor.y=element_blank())

#facet by A-D and 1-4
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='white') + 
     theme_minimal() +
     xlim(-100,100) +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD))

# lengthening facet labels

idAD_lookup <- c(
  A = "A freq i-same",
  B = "B freq i-diff",
  C = "C mort i-same",
  D = "B mort i-diff"
)

id14_lookup <- c(
  "1" = "1 nocost nodisp",
  "2" = "2 costs nodisp",
  "3" = "3 nocost disp",
  "4" = "4 costs disp"
)

#colrs <- c("no_difference"=rgb(210,210,210,max=255),"rotation"=rgb(113,166,89,max=255),"sequence"=rgb(137,117,202,max=255))
colrs <- c("no_difference"=rgb(255,255,255,max=255),"rotation"=rgb(2,98,215,max=255),"sequence"=rgb(227,0,169,max=255))

#facet by A-D and 1-4
ggplot(df_res_16, aes(x=rot_minus_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-100,100) +
     xlab("advantage of rotations over sequence in generations") +
     theme(panel.grid.minor.y=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD), labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

# p2 + facet_grid(vore ~ conservation, labeller = labeller(
#   .default = capitalize,
#   conservation = conservation_status
# ))

#df_res_16 %>% group_by(id12) %>% tally()
